Sketching for Density Estimation

### 2018-11-16 density.tex
fixed theorems

\noindent The conjectures appear to be provable in almost exactly the same manner
\begin{conjecture}
For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{2,F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{2,F} \le O(\sqrt{d_1d_2\log(d_1 + d_2) })$.
\end{conjecture}
\begin{conjecture}
For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of 
signs $s_1,...,s_n$ such that $||\sum_i s_i x_i x^T||_2 \le d\sqrt{\log{d}}$.
Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. \el{This us weak. It really should be $\sqrt{d}$ or at most $\sqrt{d\log{d}}$ }
\end{conjecture}

>>>>

\noindent The following theorems are provable in almost exactly the same manner
\begin{conjecture}
For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{F} \le O(\sqrt{d_1d_2})$.
\end{conjecture}

\begin{theorem}
For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{2} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{2} \le O(\sqrt{\log(d_1 + d_2) d_1d_2})$.
Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. 
\end{theorem}

\begin{theorem}
For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of 
signs $s_1,...,s_n$ such that $||\sum_i s_i x_i x^T||_2 \le d$.
Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. 
\end{theorem}
